|

### 2021-10-01 03-Chp-Systematic-Review.Rmd
End of day:

There were XXX primary studies <!-- TODO check this -->that contained information on this relationship. I found that statins reduce the risk of Alzheimer's disease, but had no effect of vascular dementia. Lipids were not associated with any outcome. The methods used in some of the primary studies meant that I was less confident in the accuracy of their results.

@@

I also searched clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials. In addition, I searched the bioRxiv and medRxiv preprint repositories using the tool developed in Chapter \@ref(sys-rev-tools-heading) to identify potentially relevant preprinted studies.

@@

Participants were screened for dementia at baseline and prevalent cases excluded. Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than <50 years of age at baseline. Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression. No limits were placed on the sample size of included studies.

@@

Inter- and intra-rater reliability during the screening stages were assessed for a 10% sub-sample of records. Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions (i.e. assessment of conistency), while inter-rater reliability involved two reviewers independently screening the same set of records (i.e. assessment of accuracy).

@@

Gwet's AC1 is defined as:

$$AC1 = \frac{observed\;agreement-chance\;agreement}{1-chance\;agreement}$$

In reference to a two-by-two table with cells A, B, C and D, it is calculated using the following:

\begin{equation}
  AC1 = \frac{\frac{A+D}{N}-e(\gamma)}{1-e(\gamma)}
  (\#eq:AC1-main)
\end{equation}

where $e(\gamma)$ is the chance agreement between raters, given as $2q(1-q)$, where

\begin{equation}
  q = \frac{(A+C)+(A+B)}{2N}
  (\#eq:AC1-supp)
\end{equation}

<!-- TODO Need to be sure of how to calculate. -->

@@

Intra- and inter-rater reliability was assessed against these cut-offs. If this assessment demonstrated issues with the screening process (defined as an AC1 of <.9), a larger proportion of records would have been dual-screened.

@@

#### Risk of bias due to missing evidence

@@

Both a fixed-effect and random-effects meta-analysis model was employed to combine the different included studies. <!-- TODO Need more information on the difference between the two approaches, and their formula here, and description of different methods and quarrels regarding distinction fixed effect vs random effects meta-analyses. --> The fixed-effect method was implemented as:

@@

\begin{equation}
  \theta_i = \mu + u_i
  (\#eq:meta-analysis-random)
\end{equation}

\begin{equation}
  weighted\ average = \frac{\sum Y_i (1/SE_i^2)}{\sum(1/SE_i^2)}
  (\#eq:meta-analysis-fixed)
\end{equation}

@@

<!-- TODO Explore how to map from simple diagnosis of hyperchol to dose response. Seems that does response needs >3 categories -->

@@

#### Sensitivity analyses

I conducted a leave-one-out analysis in order to explore the impact of any results on the summary effect estimate. <!-- TODO CITATION NEEDED --> In addition, where there was evidence of heterogeneity between results included in a meta-analysis, I investigated this further using meta-regression against reported characteristics. _A priori_, I was interested in the effect that the age at baseline, sex and risk-of-bias judgement had on the results. <!-- TODO Need more here -->

@@

#### Visualisation of results

@@

One of the limitations of current risk-of-bias assessments in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.

In response to this criticism, I developed a new visualisation tool was designed to allow for "paired" forest plots, as recommended by the ROB2 publication, where the risk-of-bias assessment is presented alongside the results.[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.

@@

<!-- TODO Cross check this with the actual numbers included -->

@@

Following de-duplication, the titles and abstracts of `r num_to_text(16109)` records were assessed for eligibility. `r num_to_text(387)` were deemed potentially eligible, and the full text records for these were accessed and screened. <!-- TODO Check these figures & Finish PRISMA -->

@@

<!-- TODO PRISMA must include reasons for exclusion - extract from Rayyan -->

@@

Following full-text screening, 87 reports describing `r n_included` unique studies met the criteria for inclusion in the review.[@ancelin2012a; @ancelin2013; @andrews2019a; @arvanitakis2008; @batty2014; @benn2017b; @bettermann2012a; @beydoun2011; @bruce2017; @burgess2017; @chao2015a; @chen2014; @chiang2007; @chitnis2015; @chou2014a; @chuang2015; @cramer2008; @dodge2011; @forti2010; @gnjidic2016; @gottesman2017; @gustafson2012; @haag2009; @hayden2006; @heartprotectionstudycollaborativegroup2002; @hendrie2015; @hippisley-cox2010a; @jick2000; @kimm2011; @kivipelto2001; @kivipelto2005a; @kuo2015; @li2004; @li2005a; @li2010; @liao2013; @liu2019a; @mainousa.g.2005; @mielke2005a; @mielke2010a; @mielke2011; @mukherjee2013; @muller2007; @noale2013; @notkola1998; @ostergaard2017; @pan2018; @parikh2011; @peters2009; @raffaitin2009; @rantanen2017; @rea2005a; @redelmeier2019; @reitz2004a; @reitz2010; @ridker2008; @ronnemaa2011; @schilling2017a; @smeeth2009a; @so2017; @solomon2007; @solomon2009a; @solomon2010; @sparks2008; @strand2013; @svensson2019; @szwast2007; @tan2003a; @tynkkynen2016; @tynkkynen2018; @wang2012; @whitmer2005a; @yang2015; @yoshitake1995; @zamrini2004; @zandi2005; @zhu2018a; @zimetbaum1992] Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.

The majority of studies were non-randomised studies with the sole two included randomised controlled trials both examining all-cause dementia. Similarly, a relatively small number of Mendelian randomisation studies were identified, and several performed a two-sample MR analysis using the same summary statistics from published GWAS, leading to complications in synthesis (see Section\@ref()).

Of the non-randomised studies examining treatments that modify lipid levels, the overwhelming majority examined statin use. For exposue studies, total cholesterol and LDL-cw were the most frequently reported lipid elements.

In terms of outcomes, the vast majority of studies examined either all-cause dementia or Alzheimer's disease, with only a small proportion examining vascular dementia (n=XXX, %). Some rarer outcome classifications such as vascular-component or mixed dementia were also investigated.

Of note, several studies provided evidence on a lipid fraction as part of a wider study on Mets. Raffatin/Ng

Many studies using electronic health records as their data source did not accurately report the diagnostic codes used to identify cases.

Midlife cholesterol levels were of particular interest, with several studies examining this age-range. <!-- TODO Talk a little bit more about age here -->

Three included reports were preprints (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterisk), one of which had subsequently been published and was captured by the primary literature search. All three included preprints were obtained from the bioRxiv preprint server and described Mendelian randomisation analyses.

Several Mendelian random studies made use of summary level data from the same published GWAS (the Global Lipids Genetics Consortium and the IGAP consortium <!-- TODO CITATION NEEDED -->). As this could incur double counting of participants, and so produce artifically precise estimates if meta-analysed, only results from one of these studies were included <!-- TODO How chosen?? -->. As discussed in Section \@ref(rev-discussion-MR), the choice was not material, as the results from all studies using these data sources were comparable.

<!--- TODO Figures and tables to include here:

-   Summary of risk of bias (not done)

--->

@@

As illustrated in Figure \@ref(fig:cohortLocations), the majority of reports described studies conducted in high-income countries.

<!----------------------------------------------------------------------------->
```{r cohortLocationsSetup, include = FALSE}
```

@@

of interest, many of the included studies were peformed in Taiwan (`r n_taiwan`), all but one of which made use of the Taiwan National Health Insurance.

@@

As discussed, the results of the risk of bias assessments are presented alongside their corresponding result.

@@

Both randomised controlled trials were considered to be at low risk of bias.

For NRSI
For NRSE

For MR studies

Additionally, Several synthesis were also assessed to be at risk of bias due to missing evidence. A key issue identified relating to bias due to missing data was the potential for the search to miss relevant Mendelian randomisation studies which had examined the association between Alzhiemer's disease and multiple risk factors. This is discussed further in Section \@ref(rev-discussion-MR).

<!-- TODO Discuss Taiwan health database as good evidence on non-Caucasian idenitiies -->

Haag is a good example of potentially missing results - number of cases of other outcoems reported, but no analysis performed.

@@

@@

@@

In contrast, a meta-analysis of prospective observational studies provided evidence of a protective effect of statins use on all-cause dementia risk (`r obsStatins$Dementia`, Figure \@ref(fig:obsStatinDementiaFig)).

@@

A single study examing the effect of HMGCR inhibition on any dementia, via a , and found weak evidence for an effect (`r mrStatin$Dementia`).

@@

* NRSE

* MR studies per 1-SD

In NRSI, statin use was associated with a reduce risk of all-cause dementia (`r obsStatins$Dementia`, Figure \@ref(fig:statinsNRSI)).

Several studies presented results per SD change in a lipid fraction.

In Mendelian randomisation studies, a similar

### Alzheimer's disease

There were no randomised trials of statin, or any other lipid regulating agent, use on Alzheimer's disease, though several observational studies reported on this outcome, providing evidence for a protective effect (`r obsStatins$AD`; Figure \@ref(fig:obsStatinADFig))

@@

<!----------------------------------------------------------------------------->
(ref:mrStatinDementia-cap) Random effects meta-analysis of LDL-c lowering via genetic HMGCR inhibition on Alzheimer's disease

(ref:mrStatinDementia-scap) Random effects meta-analysis of LDL-c lowering via genetic HMGCR inhibition on Alzheimer's disease

```{r mrStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrStatinDementia-cap)', out.width='100%', fig.scap='(ref:mrStatinDementia-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/fp_MR_HMGCR_AD.png"))
```
<!----------------------------------------------------------------------------->

@@

@@

@@

@@

@@

@@

### Sensitivity analysis

Given that the majority of the studies included in the review were of

@@

<!-- -   Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were -->
<!-- -   Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published studies difficult -->

There was little evidence of publication bias across the evidence base (Figure \@ref(fig:funnelStatinsAny)).

@@

<!-- TODO Will have to get actual numbers for this section -->

As show in Figure \@ref(prisma-flow-fig), the number of hits returned by the preprint searching was not substantial (bioRxiv = 256, medRxiv = 0). From these hits, three preprints were included in the review as reports of eligible studies, of which two were unique reports not captured by the main search.

For the analysis of XX on YYY, preprints added ...

Investigation of the publication status of the two unique preprints indicated that one has since been published (in late 2019 date).<!-- TODO check publication date -->

<!-- QUESTION Can I explore the amount of information added by the preprints quantitatively using the weights in the meta-analysis -->

@@

@@

@@

@@

<!----------------------------------------------------------------------------->
(ref:mrDuplication-cap) Summary of duplication of Mendelian randomisation studies which used summary statistics from the Global Lipid Genetics Consortium (GLGC) and the International Genomics of Alzheimer's Project (IGAP). Note that the Alzheimer’s Disease Genetics Consortium (ADGC) is one of the component consortia of IGAP.

(ref:mrDuplication-scap) Summary of duplication of Mendelian randomisation studies

@@

As highlighted in Section \@ref(diverse-sources-preprints), this review explicitly sought to synthesize evidence across different publication statuses (preprinted vs. published). Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint serves related to health and biomedical sciences were search as part of this review (see Appendix \@ref(appendix-medrxivr-code) for the code used to search the repositories). There were several relevant preprints captured by the search. The added evidential value of including these preprints was highlighted in Section \ref(sys-rev-including-preprints-res).

Three relevant preprints were identified

medRxiv grew out of the Epidemiology and Clinical Trials categories of the bioRxiv preprint server. The small number of studies return by the searches (or the absence of any hits in the medRxiv database - see Figure \@ref(fig:prisma-flow-fig)) is due to the timing of the preprint searches. The searches for this review were performed in mid-July 2019, but the first medRxiv preprint was registered on 25th June 2019. As such, at the point it was searched, the medRxiv database contained only a small number of records (n=`r n_at_search["med"]`).

Of the three identified preprints, two were subsequently published as of September 2020. This fits well with the analysis presented in Section \@ref(medrxivr-limitations) that, allowing for a two-year lag, approximately two-thirds of preprints are published.

While none of the preprints contributed uniquely to the review, this is again. Consider the example of one of the Mendelian randomisation analyses of the effect of LDl-c on Alzheimer's disease, which found no impact of LDL-c on AD following removal of APOE4. The manuscript was initially published in bioRxiv in July 2017[@zhu2017] which was subsequently published in Nature Communications in January 2018, following peer-review.[@zhu2018] While this study was captured by both the preprint and published searches in this review, had the searches been run within this window, the preprint would have contributed unique data to the review. This illustrates that while it may not have aided this review, if the aim is to find the current state of the art in the topic area at the time of searching, inclusion of preprints is a necessity.

>>>>

There were `n_included` primary studies that contained information on this relationship. I found that statins reduce the risk of Alzheimer's disease, but had no effect of vascular dementia. Lipids were not associated with any outcome. The methods used in some of the primary studies meant that I was less confident in the accuracy of their results.

@@

I also searched clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials. In addition, I searched the bioRxiv and medRxiv preprint repositories using the tool developed in Chapter \@ref(sys-rev-tools-heading) to identify potentially relevant preprinted studies (see Appendix \@ref(appendix-medrxivr-code) for the code used to search these preprint repositories).

@@

Participants were screened for dementia at baseline and prevalent cases excluded. Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than 50 years of age at baseline. Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression. No limits were placed on the sample size of included studies.

@@

Inter- and intra-rater reliability during the screening stages were assessed for a 10% sub-sample of records. Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions (i.e. assessment of consistency), while inter-rater reliability involved two reviewers independently screening the same set of records (i.e. assessment of accuracy).

@@

@@

Intra- and inter-rater reliability was assessed against these cut-offs. If this assessment demonstrated issues with the screening process (defined as an AC1 of less than .9), a larger proportion of records would have been dual-screened.

@@

#### Risk of bias due to missing evidence {#methods-rob-me}

@@

A random-effects meta-analysis model was employed to combine the different included studies. <!-- TODO Need more information on the difference between the two approaches, and their formula here, and description of different methods and quarrels regarding distinction fixed effect vs random effects meta-analyses. --> The fixed-effect method was implemented as:

@@

Results were stratified into subgroups on the basis of the overall risk of bias assessment, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed. Additional descriptive statistics are presented, while prediction intervals are shown as a dotted line around the overall effect estimate. Finally, a test subgroup differences between studies at different levels of risk of bias was performed (see subsequent Section \@ref(sys-rev-visualising-results)).

[Do I need to include]

Random-effects analyses assume that differences in study design and execution mean that the study effects are normally distributed around a common treatment effect ($\mu$) with a variance of $\tau^2$

\begin{equation}
  \theta_i \sim \mathcal{N}(\mu, \tau^2) (\#eq:eq9)
\end{equation}

Random-effects methods estimate $\tau^2$ to estimate the common effect ($\mu$). There are many estimators of $\tau^2$ with varying assumptions [@Veroniki2016; @Bakbergenuly2020], the details of which are beyond the scope of this article. The estimate of $\tau^2$ is incorporated into the weighting of each study

\begin{equation}
  w_i = \frac{1}{v_i + \hat{\tau^2}} (\#eq:eq10)
\end{equation}

<!-- A random-effects meta-analysis allows for study-specific effects, and assumes that the true effect estimated by each study varies and is assumed to be randomly and normally distributed on the transformed scale (e.g. log-ORs) between studies, with a variance of 𝜏2. The between-study variance is estimated (usually using the “method of moments” or DerSimonian and Laird estimate), and used to modify the weights of studies when calculating the summary effect estimate and variance. The weight of each study is 1𝑣𝑖+𝜏2 where 𝑣𝑖 is the variance of the 𝑖𝑡ℎ study and 𝜏2 is the estimate of the between-study variance. So long as the between-study variance is larger than 0, smaller studies will be given more weight in random-effects meta-analysis than in a fixed-effect meta-analysis. If the between-study variance is 0, then the random-effects model is equivalent to the fixed-effect model. -->
<!-- In both fixed-effect and random-effects inverse-variance meta-analysis, the summary effect estimate and variance are estimated in the same way. The effect estimates (𝜃𝑖) from each study can be (transformed) ORs, relative risks (RRs), standardised mean differences (SMDs) or other types of estimates: -->
<!-- 𝜃̂𝑆𝑢𝑚𝑚𝑎𝑟𝑦=⁡Σ𝑤𝑖𝜃𝑖Σ𝑤𝑖 -->
<!-- (2) -->
<!-- 𝑉𝑎𝑟𝑖𝑎𝑛𝑐𝑒⁡𝑜𝑓⁡𝜃̂𝑆𝑢𝑚𝑚𝑎𝑟𝑦=⁡1Σ𝑤𝑖 -->
<!-- (3) -->
<!-- where 𝜃𝑖 is effect estimate and 𝑤𝑖 is the weight from the 𝑖𝑡ℎ study on an approximately normal scale. -->

<!-- \begin{equation} -->
<!--   \theta_i = \mu + u_i -->
<!--   (\#eq:meta-analysis-random) -->
<!-- \end{equation} -->

<!-- \begin{equation} -->
<!--   $weighted\ average = \frac{\sum Y_i (1/SE_i^2)}{\sum(1/SE_i^2)}$ -->
<!--   (\#eq:meta-analysis-fixed) -->
<!-- \end{equation} -->

@@

@@

#### Additional analyses

Where there was evidence of heterogeneity between results included in a meta-analysis, I investigated this further using meta-regression against reported characteristics. _A priori_, I was interested in the effect that the age at baseline, sex and risk-of-bias judgement had on the results. <!-- TODO Need more here -->

@@

#### Visualisation of results {#sys-rev-visualising-results}

@@

One of the limitations of current risk-of-bias assessments in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis. In response to this criticism, I developed a new visualisation tool was designed to allow for "paired" forest plots, as recommended by the ROB2 publication, where the risk-of-bias assessment is presented alongside the results.[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.

@@

@@

Following de-duplication, the titles and abstracts of `r num_to_text(16109)` records were assessed for eligibility. `r num_to_text(387)` were deemed potentially eligible, and the full text records for these were accessed and screened.

@@

@@

Following full-text screening, `r n_reports_included` reports describing `r n_included` unique studies met the criteria for inclusion in the review.[@ancelin2012a; @ancelin2013; @arvanitakis2008; @batty2014; @benn2017b; @bettermann2012a; @beydoun2011; @bruce2017; @burgess2017; @chao2015a; @chen2014; @chiang2007; @chitnis2015; @chou2014a; @chuang2015; @cramer2008; @dodge2011; @forti2010; @gnjidic2016; @gottesman2017; @gustafson2012; @haag2009; @hayden2006; @heartprotectionstudycollaborativegroup2002; @hendrie2015; @hippisley-cox2010a; @jick2000; @kimm2011; @kivipelto2001; @kivipelto2005a; @kuo2015; @li2004; @li2005a; @li2010; @liao2013; @liu2019a; @mainousa.g.2005; @mielke2005a; @mielke2010a; @mielke2011; @mukherjee2013; @muller2007; @noale2013; @notkola1998; @ostergaard2017; @pan2018; @parikh2011; @peters2009; @raffaitin2009; @rantanen2017; @rea2005a; @redelmeier2019; @reitz2004a; @reitz2010; @ridker2008; @ronnemaa2011; @schilling2017a; @smeeth2009a; @so2017; @solomon2007; @solomon2009a; @solomon2010; @sparks2008; @strand2013; @su2017; @svensson2019; @szwast2007; @tan2003a; @tynkkynen2016; @tynkkynen2018; @wang2012; @whitmer2005a; @yamada2009b; @yang2015; @yoshitake1995; @zamrini2004; @zandi2005; @zhu2018a; @zimetbaum1992] Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.

The majority of included studies described non-randomised analyses, with the sole two included randomised controlled trials (the Heart Protection Study/British Heart Foundation trial,[@heartprotectionstudycollaborativegroup2002] and the JUPITER trial[@ridker2008]) both examining statins use on all-cause dementia in older adults. A similarly small number of Mendelian randomisation studies were identified, several of which employed a two-sample approach using the identical summary statistics from published GWAS, leading to complications in the synthesis (see Section \@ref(res-AD)).

Of the `r_nrsi_included` non-randomised studies examining treatments that modify lipid levels, all examined statin use (`r n_statins`), while a small number also examined other non-statins agents such as fibrates (`r n_fibrates`). In the `r n_nrse_included` non-randomised studies of exposure, hypercholesterolemia `r n_hyperchol` and `r n_TC` were the most frequently reported risk factors.

In terms of outcomes, the vast majority of studies examined either all-cause dementia (`r n_Dementia`) or Alzheimer's disease (`r n_AD`), with only a small proportion examining vascular dementia `r n_VaD`. Some rarer outcome classifications such as vascular-component or mixed dementia were also investigated.

<!-- Many studies using electronic health records as their data source did not accurately report the diagnostic codes used to identify cases. -->

<!-- Midlife cholesterol levels were of particular interest, with several studies examining this age-range.  -->

<!--- TODO Talk a little bit more about age here --->

Three included reports were preprints (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterisk),[@ridker2008; @so2017;@zhu2017] one of which had subsequently been published and was captured by the primary literature search.[@zhu2018] All three included preprints were obtained from the bioRxiv preprint server and described a Mendelian randomisation analysis.

<!-- As discussed in Section \@ref(rev-discussion-MR), the choice was not material, as the results from all studies using these data sources were comparable. -->

<!-- TODO Figures and tables to include here: -   Summary of risk of bias (not done) -->

@@

```{r cohortLocationsSetup, include = FALSE}
```

As illustrated in Figure \@ref(fig:cohortLocations), the majority of reports described studies conducted in high-income countries. Of interest, several of the included studies were conducted in Taiwan (`r n_taiwan`), all but one of which made use of the Taiwan National Health Insurance database.

@@

Finally, several eligible studies reported as conference abstracts did not present numerical results. These reports were included in the analysis to enable assessment of risk of bias due to missing evidence (see Section \@ref(methods-rob-me)).

&nbsp;<!----------------------------------------------------------------------->

@@

As discussed above, the results of the risk-of-bias assessments are presented alongside their corresponding result. A more detailed discussion fo the sources and directions of bias is presented in Chapter \@ref(tri-heading), and so this section

@@

<!-- Both randomised controlled trials were considered to be at low risk of bias.  -->

<!-- For NRSI, common biases include immortal time (where participants in the exposure group are followed up) -->
<!-- For NRSE  -->

<!-- For MR studies, concerns over potential genetic pleiotropy -->

<!-- Additionally, several synthesis were also assessed to be at risk of bias due to missing evidence.  -->

<!-- A key issue identified relating to bias due to missing data was the potential for the search to miss relevant Mendelian randomisation studies which had examined the association between Alzhiemer's disease and multiple risk factors. This is discussed further in Section \@ref(rev-discussion-MR). -->

<!-- Several eligible studies included in the analysis did not have available results, either due to selective reporting of significant results in conference abstracts,[@su2017; @yamada2009b] or due to the unavailability of supplementary materials containing the relevant results.[@haag2009] -->

@@

```{r Hypercholesterolemia, include = FALSE, message=FALSE, warning=FALSE}
```

```{r mrLipidsAD, include = FALSE, message=FALSE, warning=FALSE}
```

```{r LipidsSD, include = FALSE, message=FALSE, warning=FALSE}
```

@@

&nbsp;<!----------------------------------------------------------------------->

@@

In contrast, a meta-analysis of `r obsStatins$Dementia$n` prospective observational studies provided evidence of a protective effect of statins use on all-cause dementia risk (`r obsStatins$Dementia$estimate`, Figure \@ref(fig:obsStatinDementiaFig)).

@@

Finally, a single Mendelian randomisation analysis was identified examining the effect of genetically lowered LDL-c levels via HMGCR inhibition on the risk of all-cause dementia, which provided weak evidence for an effect (`r mrStatin$Dementia$estimate`).

@@

Across all outcomes, lipid levels were categorised in a number of ways. The most common categorisation was hypercholesterolemia at baseline, defined most frequently as a total cholesterol measurement of greater than 6.5 mmol/L.

`r obsHyperchol$Dementia$n` studies reported on the association of hypercholesterolemia with all-cause dementia and provided weak evidence for an effect (`r obsHyperchol$Dementia$estimate`, Figure \@ref(fig:obsHyperDementia))

<!----------------------------------------------------------------------------->
(ref:obsHyperDementia-cap) __shortcap:__

(ref:obsHyperDementia-scap) shortcap

```{r obsHyperDementia, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperDementia-cap)', out.width='100%', fig.scap='(ref:obsHyperDementia-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_Dementia.png"))
```
<!----------------------------------------------------------------------------->

Several studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction. Very weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$Dementia_TC)`), LDL-c (`r n_effect(obsLipids$Dementia_HDL)`), HDL-c (`r n_effect(obsLipids$Dementia_HDL)`) or triglycerides (`r n_effect(obsLipids$Dementia_HDL)`). Forest plots for these analyses are presented in Appendix \@ref(lipid-fraction-forest-plots).

Finally, there were no identified Mendelian randomisation analysis examining the effect of lipid levels on all-cause dementia risk.

&nbsp;<!----------------------------------------------------------------------->

### Alzheimer's disease {#res-AD}

There were no randomised trials of statin, or any other lipid regulating agent, use on Alzheimer's disease, though several observational studies reported on this outcome and provid evidence for a protective effect (`r n_effect(obsStatins$AD)`; Figure \@ref(fig:obsStatinADFig)).

@@

<!----------------------------------------------------------------------------->
(ref:mrStatinAD-cap) Random effects meta-analysis of LDL-c lowering via genetic HMGCR inhibition on Alzheimer's disease

(ref:mrStatinAD-scap) Random effects meta-analysis of LDL-c lowering via genetic HMGCR inhibition on Alzheimer's disease

```{r mrStatinADFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrStatinAD-cap)', out.width='100%', fig.scap='(ref:mrStatinAD-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/fp_MR_HMGCR_AD.png"))
```
<!----------------------------------------------------------------------------->

@@

`r obsHyperchol$AD$n` studies reported on the association of hypercholesterolemia with all-cause dementia and provided weak evidence for an effect (`r obsHyperchol$AD$estimate`, Figure \@ref(fig:obsHyperAD))

<!----------------------------------------------------------------------------->
(ref:obsHyperAD-cap) __shortcap:__

(ref:obsHyperAD-scap) shortcap

```{r obsHyperAD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperAD-cap)', out.width='100%', fig.scap='(ref:obsHyperAD-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_AD.png"))
```
<!----------------------------------------------------------------------------->

Similarly to all-cause dementia everal studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction. Very weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$AD_TC)`), LDL-c (`r n_effect(obsLipids$AD_HDL)`), HDL-c (`r n_effect(obsLipids$AD_HDL)`) or triglycerides (`r n_effect(obsLipids$AD_HDL)`). Forest plots for these analyses are presented in Appendix \@ref(lipid-fraction-forest-plots).

Finally, there were several identified Mendelian randomisation studies examining the effect of genetically lowered LDL-c on Alzheimer's disease risk (Figure \ref(mrDuplication)). However, all of these studies used a two-sample approach, making use of summary statistics from the GLGC and IGAP consortia. Due to this overlap, which would result in a falsely precise estimate caused by multiple counting of participants, no meta-analysis of these studies was performed. However, across all analysis, using varying number of SNPS, no evidence for an effect was observed (Figure \ref(mrDuplication)).

<!----------------------------------------------------------------------------->
(ref:mrDuplication-cap) Summary of duplication of Mendelian randomisation studies which used summary statistics from the Global Lipid Genetics Consortium (GLGC) and the International Genomics of Alzheimer's Project (IGAP). Note that the Alzheimer’s Disease Genetics Consortium (ADGC) is a sub-cohort within IGAP.

(ref:mrDuplication-scap) Summary of duplication across two sample Mendelian randomisation studies

@@

As noted above, there was substantially less literature available on the association of my risk factors of interest and vascular dementia.

There were no randomised trials for this outcome. `r num_to_text(obsStatins$VaD$n,T)` prospective cohort studies examined statin use and vascular dementia, though meta-analysis of these studies provided very weak evidence for an effect (`r n_effect(obsStatins$VaD)`; Figure \@ref(fig:obsStatinVaDFig)).

@@

A single Mendelian randomisation analysis was identified that examining the effect of genetically lowered LDL-c levels via HMGCR inhibition on the risk of vascular dementia, which provided weak evidence for an effect (`r mrStatin$VaD$estimate`).

@@

`r obsHyperchol$VaD$n` studies reported on the association of hypercholesterolemia with all-cause dementia and provided weak evidence for an effect (`r obsHyperchol$VaD$estimate`, Figure \@ref(fig:obsHyperVaD))

<!----------------------------------------------------------------------------->
(ref:obsHyperVaD-cap) __shortcap:__

(ref:obsHyperVaD-scap) shortcap

```{r obsHyperVaD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperVaD-cap)', out.width='100%', fig.scap='(ref:obsHyperVaD-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_VaD.png"))
```
<!----------------------------------------------------------------------------->

Similarly to all-cause dementia everal studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction. Very weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$VaD_TC)`), LDL-c (`r n_effect(obsLipids$VaD_HDL)`), HDL-c (`r n_effect(obsLipids$VaD_HDL)`) or triglycerides (`r n_effect(obsLipids$VaD_HDL)`). Forest plots for these analyses are presented in Appendix \@ref(lipid-fraction-forest-plots).

Finally, there were no identified Mendelian randomisation analysis examining the effect of lipid levels on vascular dementia risk.

@@

<!-- TODO Can only do meta-regression in analysis with 10 studies, so statins and hypercholesterolemia should -->

Across all analysis with

@@

@@

<!--    Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were -->
<!--    Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published studies difficult -->

There was little evidence of small study effects across the evidence base (Figure \@ref(fig:funnelStatinsAny)).

@@

As show in Figure \@ref(prisma-flow-fig), the number of hits returned by the preprint searching was not substantial (bioRxiv = 256, medRxiv = 0). From these hits, three preprinted reports of eligible studies were included in the review, of which two described unique studies not captured by the main search.[@andrews2019a; @so2017]

All identified preprinted studies were. However, including preprints did provide useful additional evidence value in a number of meta-analysis. For example, re-analysing the results of available for the effect of HMGCR SNPS on Alzheimer's disease (Figure \@ref) in Mendelian randomisation studies, illustrates that the result only available from a preprint contributed `r mrStatinPreprintWeight` of the weight in a fixed-effect meta-analysis.

<!----------------------------------------------------------------------------->
(ref:preprintWeights-caption) Amount of information added by inclusion of preprinted results, estimated from the weight assigned to the study in a random-effect meta-analysis

(ref:preprintWeights-scaption) Added information due to inclusion of preprints

```{r preprintWeights-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

<!-- TODO Add extra column with details of Figure showing met-analysis -->

Investigation of the publication status of the two unique preprints indicated that one has since been published (in late 2019 date),[@andrews2019; @andrews2021]. The final preprint has not yet been published.[@so2017]

@@

<!-- TODO Talk about problems with including Hippsley-Cox re double-counting -->

@@

Generalisability was aided by the large number of studies performed using the Taiwan health database, which represents a good sources of evidence on non-Caucasian populations

@@

<!----------------------------------------------------------------------------->
(ref:mrAssumptions-cap) Summary of the assumptions in Mendelian randomisation analyses: (I) _relevance_ - the genetic variant associates with the risk factor of interest; (II) _independence_ - the variant-exposure association has no unmeasured confounders; and (III) _exclusion restriction_ - variants affect the outcome only through their effect on the risk factor of interest (i.e. there is no horizontal pleiotropy).

(ref:mrAssumptions-scap) Overview of assumptions in Mendelian randomisation analyses

```{r mrAssumptions, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrAssumptions-cap)', out.width='100%', fig.scap='(ref:mrAssumptions-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/mrAssumptions.png"))
```
<!----------------------------------------------------------------------------->

@@

@@

As highlighted in Section \@ref(diverse-sources-preprints), this review explicitly sought to synthesize evidence across different publication statuses (preprinted vs. published). Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint serves related to health and biomedical sciences were search as part of this review.  The small number of studies return by the searches (or the absence of any hits in the medRxiv database - see Figure \@ref(fig:prisma-flow-fig)) is due to the timing of the preprint searches. The searches for this review were performed in mid-July 2019, but the medRxiv repository, an offshoot of the Epidemiology and Clinical Trials categories of the bioRxiv preprint server, only registered its first preprint 25th June 2019. As such, at the point it was searched, the medRxiv database contained only a very small number of records (n=`r n_at_search["med"]`).
